Distinction Centrality Analysis

### 2025-07-19 analysis.qmd
caveman

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "distinction.new.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

## Broker Computatinal Experiements

@@

```{r}
   library(patchwork)
   library(ggraph)
   gg <- function(x, lay.o = "kk", star = 1) {
      n <- vcount(x)
      V(x)$name <- 1:n
      c <- c(rep("tan2", n))
      c[star] <- "blue"
      gk <- which(degree(x) == 4)
      gk <- gk[gk != star]
      c[gk] <- "red"
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) +
      ylim(-4, 3.5) + xlim(-4, 3.25) 
      return(w)
      }
   p.list <- lapply(b, gg)
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:6)], nrow = 2)
   ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
```

@@

```{r}
   make.broker.cliques <- function(n = 10) {
      g1 <- make_full_graph(4, directed = FALSE)
      g2 <- make_full_graph(4, directed = FALSE)
      g3 <- g1 + g2
      g3 <- add_vertices(g3, 1)
      g3 <- g3 + edge(9,4)
      g3 <- g3 + edge(9,5)
      el <- vector(mode = "list", length = n)
      el[[1]] <- g3
      a <- 10
      for (i in 2:n) {
         g3 <- g3 + make_full_graph(4, directed = FALSE)
         g3 <- g3 + edge(9,a)
         el[[i]] <- g3
         a <- a + 4
         }
   return(el)
   }
   b <- make.broker.cliques(30)
   b.r <- lapply(b, function(x) {rewire(x, each_edge(p = .05, loops = FALSE, multiple = FALSE))})
   c <- lapply(b, distinction.new, norm = FALSE)
```

@@

```{r}

```

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "distinction.new.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "make.broker.cliques.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(12345)
   b <- connect.caves(c = 4, nc = 4, n = 20)
   c <- lapply(b, distinction.new, norm = FALSE)
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      c <- c(rep("tan2", n))
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      #ylim(-4, 3.5) + xlim(-4, 3.25) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
```

## Broker Computational Experiements

@@

```{r}
   library(patchwork)
   library(ggraph)
   p.list <- lapply(b, gg)
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:6)], nrow = 2)
   ggsave(here("Plots", "tree-examples.png"), width = 12, height = 8, units = "in")
```

@@

@@
